### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@1ab5ab8b4e8faed361f60000cf175df3738839b2 🚀

\hypertarget{metaweb-model}{%
\section{Metaweb Model}\label{metaweb-model}}

@@

\hypertarget{spatiotemporally-explicit-networks}{%
\section{Spatiotemporally Explicit
Networks}\label{spatiotemporally-explicit-networks}}

@@

\hypertarget{sampling-prioiritization}{%
\section{Sampling Prioiritization}\label{sampling-prioiritization}}

How do we improve out udnerstanding of this pollination network, or
determine if it is changing over time?

@@

\hypertarget{discussion}{%
\section*{Discussion}\label{discussion}}
\addcontentsline{toc}{section}{Discussion}

>>>>

\hypertarget{predicting-the-metaweb}{%
\section{Predicting the metaweb}\label{predicting-the-metaweb}}

@@

\hypertarget{predicting-networks-in-space-and-time}{%
\section{Predicting networks in space and
time}\label{predicting-networks-in-space-and-time}}

@@

\hypertarget{prioritizing-spatial-sampling-of-pollinator-interactions}{%
\section{Prioritizing spatial sampling of pollinator
interactions}\label{prioritizing-spatial-sampling-of-pollinator-interactions}}

How do we improve out understanding of this pollination network, or
determine if it is changing over time?

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

We predict things alright. Emphasizes how heterogenous data sources can
improve interaction prediction (rocpr fig). Advances network embedding
as a framework for prediction of species interaction networks.
